Copulas and their potential for ecology

### 2019-12-13 Paper.Rmd
some more working on responses for AER

>>>>

<!--para on data requirements of the methods, requested by the AER referees-->
Data requirements for copula methods will vary depending on multiple factors,
but our results show that data requirements are not beyond what is common 
in ecology. With copula methods as with any statistical analysis, the data required to detect 
an effect or a phenomenon depends on the strength of the effect. For instance,
detection of mild asymmetry of tail association will require more data than
detection of strong asymmetry. Different copula or copula-related methods will
also require different amount of data. For instance, our nonparametric methods 
such as the partial Spearman correlation should be effective with datasets 
only slightly bigger than typical guidelines for standard correlation 
methods; whereas our model-selection approaches may be most effective with more data.
Some of our datasets were large, but others were much smaller, e.g., aphid datasets
comprised 30 points, and our analyses still provided robust results. Thus
many copula methods will be suitable for datasets of sizes that are common in ecology.
The partial Spearman correlation seems particularly widely applicable.
